Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 response.md

Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1. However, the original verseion of Equation 4 could produce vote fractions greater than 1 if left in the same form as Equation 2. We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader. Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II, as well as Minor Comment 3). All data in the tables and catalog have been updated to account for these small changes.

----------------------------------
Minor Comment 5
----------------------------------

***5) Figure 8: "-10 < log(xi) < 10" should be "-10 < xi < 10"***

Correct, thank you. This typo has been edited in the figure caption.

@@

***response pending final fit ***

----------------------------------
Minor Comment 7
----------------------------------

***7) Section 4.2: "The boundaries [of the convex hull] are then adjusted until the contamination from both groups is minimized." If I look at Figure 9, it would appear that the correctable and lower-limit regions can be perfectly separated (using a tree, for instance). Am I wrong about this?***

The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in f_features-redshift space, but there are a few regions near the edges in which there is overlap between the two populations. This is affected slightly in Figure 9 by the choice of bin size and location. However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f. Implementing a convex hull in this space created a very small volume near the edge of the inner convex hull that had overlapping positive and negative data points; we optimize the overall accuracy of the hull by adjusting the outer boundaries as described in what is now Section 4.1.

Use of a different method such as a tree could potentially prove to be a superior separator. However, the new normalization technique used in this draft results in very clean separation based on the convex hull, with only a single adjustment (see https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb). Further optimization would have an extremely minimal effect on the overall results.

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Choice of five quintiles (MiC 8). See #184.

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
cannot be confidently assigned, the \emph{range} of debiased values is
estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
values for any given observed \ffeatures{} value, again as a function of
surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
we compute the spread of
intrinsic values of \ffeaturesrest{} for five quantiles of observed \ffeatures{}
(corresponding to the ``clean'' thresholds used in prior GZ publications).
\hl{The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
enclosing the inner 68\% of the data. This range is represented by the orange bars in 
Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
cannot be directly debiased by the $\zeta$ method, these ranges are used to
denote the upper and lower limits on the expected values \ffeaturesrest{} as a
function of the observed \ffeatures.

>>>>

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
cannot be confidently assigned, the \emph{range} of debiased values is
estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
values for any given observed \ffeatures{} value, again as a function of
surface brightness and redshift. \changes{In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
we compute the spread of
intrinsic values of \ffeaturesrest{} for five quantiles of observed \ffeatures{}
(corresponding to the ``clean'' thresholds used in prior GZ publications).
The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
enclosing the inner 68\% of the data. This range is represented by the orange bars in 
Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
cannot be directly debiased by the $\zeta$ method, these ranges are used to
denote the upper and lower limits on the expected values \ffeaturesrest{} as a
function of the observed \ffeatures.
